A finite-state morphological transducer for Kyrgyz

### 2012-03-21 paper/paper.tex
things that eval taught us`

>>>>

%FIXME: new stuff
The evaluation has brought to light some systematic issues with the transducer.  One such issue is that mono-syllabic verbs ending in vowels
(e.g., [же] \eng{eat}, [жуу] \eng{wash}, [оо] \eng{tilt})
do not take a gerund/infinitive in -/Uː/, but are only used with the morphologically, semantically, and syntactically similar -/(I)ш/ suffix.  To prevent these forms from being output, a different version of the current verbal continuation lexica should be made to capture the morphological difference---i.e., forms of these verbs that are marked as \texttt{<ger>} should be output with the -/(I)ш/ suffix instead of the -/Uː/ suffix.

A similar issue the gold standard developed for evaluation showed us was that not all adjectives can be used used as adverbs; the transducer currently assumes they can, and every item in the adjective lexicon currently also has an adverbial reading.  While usually only morphologically complex (i.e., derived) adjectives are restricted from being used as adverbs, our initial strategy for fixing this will involve making a separate ``no adverb reading'' lexicon for adjectives that cannot be used as adverbs.
